\bf Range Analysis for the IonMonkey JavaScript engine

### 2012-05-02 project-writings/paper.tex
A bunch more evaluation.

\caption{Selected range arithmetic definitions}
\label{fig:range_arith}
\end{figure}

@@

\begin{figure}[ht]
\begin{eqnarray*}
\Squash(n) &=& \begin{cases}
 -2^{31} &\text{if } n = -\infty \\
2^{31}-1 &\text{if } n = \infty \\
n&\text{otherwise } \\
\end{cases}\\
\Squash([l, h]) &=& [\Squash(l), \Squash(h)]
\end{eqnarray*}
%
\begin{eqnarray*}
x = \Phi(y, z) &\Rightarrow&
    \Range(x) = \Squash(\Range(y)) \cup \Squash(\Range(z)) \\
x = \beta(y, [l, h]) &\Rightarrow& \Range(x) = \Squash(\Range(y)) \cap [l, h] \\
x = y + z &\Rightarrow& \Range(x) = \Squash(\Range(y)) + \Squash(\Range(z)) \\
x = y - z &\Rightarrow& \Range(x) = \Squash(\Range(y)) - \Squash(\Range(z)) \\
x = y \x z &\Rightarrow& \Range(x) = \Squash(\Range(y)) \x \Squash(\Range(z)) \\
x = c &\Rightarrow& \Range(x) = [c, c]
\end{eqnarray*}
\caption{Selected range analysis equations}
\label{fig:range_anal}
\end{figure}

@@

These results show that our range analysis is generally quite
successful in eliminating overflow checks from programs, but our
timing results indicate that this does yield that substantial of a
performance improvement. We believe that this is because the overhead
of an essentially never taken branch on modern hardware are quite
low. While on a microbenchmark we constructed overflow check
elimination resulted in a substantial (around 30\%) speedup, it appears that
this does not translate well to more realistic code.

>>>>

\caption{Range arithmetic definitions}
\label{fig:range_arith}
\end{figure}

@@

\begin{figure}[ht]
\begin{eqnarray*}
\Squash(n) &=& \begin{cases}
 -2^{31} &\text{if } n = -\infty \\
2^{31}-1 &\text{if } n = \infty \\
n&\text{otherwise } \\
\end{cases}\\
\Squash([l, h]) &=& [\Squash(l), \Squash(h)]
\end{eqnarray*}
%
\begin{eqnarray*}
x = \Phi(y, z) &\Rightarrow&
    \Range(x) = \Squash(\Range(y)) \cup \Squash(\Range(z)) \\
x = \beta(y, [l, h]) &\Rightarrow& \Range(x) = \Squash(\Range(y)) \cap [l, h] \\
x = y + z &\Rightarrow& \Range(x) = \Squash(\Range(y)) + \Squash(\Range(z)) \\
x = y - z &\Rightarrow& \Range(x) = \Squash(\Range(y)) - \Squash(\Range(z)) \\
x = y \x z &\Rightarrow& \Range(x) = \Squash(\Range(y)) \x \Squash(\Range(z)) \\
x = c &\Rightarrow& \Range(x) = [c, c]
\end{eqnarray*}
\caption{Range analysis equations}
\label{fig:range_anal}
\end{figure}

@@

These results show that our range analysis is generally quite
successful in eliminating overflow checks from programs, but our
timing results indicate that this does yield that substantial of a
performance improvement. We believe that this is because the overhead
of an essentially never taken branch on modern hardware are quite
low. While on a microbenchmark we constructed overflow check
elimination resulted in a substantial (!30\%) speedup, it appears that
this does not translate well to more realistic code.
